---
title: "ECON432 HW5 R Exercises"
author: "YUANJIAN ZHOU"
date: "Mar 10,2020"
output:
  html_document:
    theme: united
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1
```{r}
library(PerformanceAnalytics)
library(fGarch)
library(tseries)
library(car)
library(quantmod)
```

## preparation
```{r}
get_price = function(tick) {
  result = suppressWarnings(
    get.hist.quote(
      instrument = tick,
      quote = "AdjClose",
      provider = "yahoo",
      start = "2000-01-03", 
      end = "2014-02-21",     
      compression = "m",
      retclass = "zoo"
    )
  )
  return(result)
}
GSPC = get_price("^GSPC")
MSFT = get_price("MSFT")
data_price = merge.zoo(GSPC, MSFT) # merge zoo objects with same index
colnames(data_price) = c("GSPC", "MSFT")
# change index to Month-Year format, like Mar 1995
index(data_price) = as.yearmon(index(data_price), "%B%y")
# rt = lnpt - lnpt-1
data_ccreturn = diff(log(data_price))
```

# (a)
```{r}
plot(data_ccreturn,
     main = "Monthly CC Return",
     xlab = "time",
     col = "purple")
```

- We can see that there is weak (or even no) time dependence, volatility clustering, and it seems both series have a lot of outliers. What'more, the series look like random walk.

## (b)
```{r}
fourplots = function(tick) {
  par(mfrow = c(2, 2))
  data = data_ccreturn[, tick]
  # return plot
  plot(data,
     main = "Monthly CC Return",
     xlab = "time",
     col = "purple")
  
  # acf
  acf(data)
  
  # density plot
  plot(
    density(data),
    type = "l",
    main = "Denstiy Plot",
    xlab = "monthly cc return",
    ylab = "probability",
    col = "purple"
  )
  
  # qqplot
  qqPlot( ~ data,
          col = "purple",
          ylab = "sample quantitles",
          main = "QQ plot")
}
```

- *MSFT*
```{r}
fourplots("MSFT")
```

- *GSPC*
```{r}
fourplots("GSPC")
```

- Both return eries do not look normally distributed.

## (c)
```{r}
jarque.bera.test(data_ccreturn$GSPC)
jarque.bera.test(data_ccreturn$MSFT)
```

- From the results, Jarque Bera Test refuses H0 that X is normally distributed for both series, that means they are not normally distributed.

## (d)
- *MSFT*
```{r}
garch_MSFT = garchFit(~garch(1,1), data = data_ccreturn$MSFT, trace = F)
summary(garch_MSFT)
```
- $\alpha + \beta = 0.13 + 0.77 = 0.9$

- *GSPC*
```{r}
garch_GSPC = garchFit(~garch(1,1), data = data_ccreturn$GSPC, trace = F)
summary(garch_GSPC)
```
- $\alpha + \beta = 0.23 + 0.75 = 0.98$

- Both series have a $\alpha + \beta \geq 0.9$, which means that both series has a very high persistence, the volatility clustering is very strong.

## (e)
- Using the summary table above:
- *GSPC*
```{r}
# for alpha
alpha_ci_95_l =  0.2308 - 1.96 * 7.527e-02
alpha_ci_95_u =  0.2308 + 1.96 * 7.527e-02
sprintf("95 percent confidence interval for alpha is [%f,%f]", alpha_ci_95_l, alpha_ci_95_u)

# for beta
beta_ci_95_l = 0.7549 - 1.96 * 7.014e-02
beta_ci_95_u = 0.7549 + 1.96 * 7.014e-02
sprintf("95 percent confidence interval for beta is [%f,%f]", beta_ci_95_l, beta_ci_95_u)

```

- *MSFT*
```{r}
# for alpha
alpha_ci_95_l =  0.1332 - 1.96 * 0.0948
alpha_ci_95_u =  0.1332 + 1.96 * 0.0948
sprintf("95 percent confidence interval for alpha is [%f,%f]", alpha_ci_95_l, alpha_ci_95_u)

# for beta
beta_ci_95_l = 0.774 - 1.96 * 0.158
beta_ci_95_u = 0.774 + 1.96 * 0.158
sprintf("95 percent confidence interval for beta is [%f,%f]", beta_ci_95_l, beta_ci_95_u)

```

## (f)
- Using the summary table above:
- *GSPC*
$$
\begin{align*}
H_0&: \alpha_1 = 0\\
t  &= \frac{0.2308-0}{0.07527} \approx 3.066>1.96 = t_{0.975}
\end{align*}
$$

- So we reject $H_0:\alpha_1 = 0$ with 95 % confidence.

$$
\begin{align*}
H_0&: \beta_1 = 0.9\\
t  &= \frac{0.7594-0.9}{0.07014} \approx -2<-1.96 = t_{0.025}
\end{align*}
$$

- So we reject $H_0:\beta_1 = 0.9$ with 95 % confidence.

- *MSFT*
$$
\begin{align*}
H_0&: \alpha_1 = 0\\
t  &= \frac{0.1332-0}{0.0948} \approx 1.41<1.96 = t_{0.975}
\end{align*}
$$

- So we can not reject $H_0:\alpha_1 = 0$ with 95 % confidence.

$$
\begin{align*}
H_0&: \beta_1 = 0.9\\
t  &= \frac{0.774-0.9}{0.158} \approx -0.8>-1.96 = t_{0.025}
\end{align*}
$$

- So we can not reject $H_0:\beta_1 = 0.9$ with 95 % confidence.