---
title: "Homework 1"
author: "YUANJIAN ZHOU"
date: "Jan 15,2020"
# date: '`r format(Sys.Date(), "%Y-%b-%d")`'
output: 
  html_document:
    toc: TRUE
    #number_sections: TRUE
    theme: united
    #highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:/Users/zyj37/Desktop/MAE/Winter/ECON 432/Homework")
library(tidyverse)
```

# 1 Part I:Review Questions

## 1

$$
R_{t} = \frac{P_{t}}{P_{t-1}}-1=\frac{46.76}{44.89}-1\approx0.042
$$

The simple monthly return between the end of December,2011 and the tend of January,2012 is **0.042**.

$$
10000*(1+0.042) = 10420
$$

The investment will be worth **10420** at the end of January 2012.

## 2

$$
r_{t} = lnP_{t} - lnP_{t-1}=ln46.76-ln44.89 \approx0.041
$$

The cc monthly return between December,2011 and January,2012 is **0.041**.

$$
R_{t} = e^{r_{t}}-1=e^{0.041}-1 \approx 0.042
$$

It is the same as the answer in **part 1**.

## 3

$$
R_{A} = (1+R_{t})^{12}-1 =(1+0.042)^{12}-1\approx 0.638
$$

The simple annual return with mothly compounding is **0.638**.

## 4

$$
r_{A} = r_{t}*12=0.041 * 12 = 0.492
$$

The cc annual return is **0.492**

## 5

$$
\begin{align*}
1 + R_{A}^{actual} &= (1+R_{t})*\cdots*(1+R_{t-11})\\
&=\frac{P_{t}}{P_{t-1}}*\cdots*\frac{P_{t-11}}{P_{t-12}}\\
&=53.10/44.89\approx1.183
\end{align*}
$$

$$
R_{A}^{actual} = 0.183\\
10000*(1+0.183) = 11830 
$$

The actual annual return between December 2011 and December 2012 is **0.183**. The investment would be worth **11830** at the end of December 2012, which is **smaller** than the result in part 3.

## 6

$$
r_{A}^{actual}=ln(\frac{P_{t}}{P_{t-12}})=ln(\frac{53.10}{44.89})\approx0.168
$$

The actual annual cc return between December 2011 and December 2012 is **0.168**.

$$
R_{t}^{actual} = e^{r_{t}^{actual}}-1=e^{0.168}-1 \approx 0.183
$$

It is the same as the answer in **part 5**.

# 2 Part II. R Exercises

## 1.
```{r}
sbux.df = read.csv("sbuxPrices.csv")
```

### 1.1
```{r}
# head is used to show the first (defualt is 6) observations in the dataframe.
head(sbux.df)
```

### 1.2
```{r}
# tail is used to show the last (defualt is 6) observations in the dataframe.
tail(sbux.df)
```

### 1.3
```{r}
# it is a slice expression to get the column "Adj.Close" from the dataframe.
sbuxPrices.df = sbux.df[,"Adj.Close",drop= F]
```

### 1.4
```{r}
# set the rownames of the dataframe
rownames(sbuxPrices.df) = sbux.df$Date
```

### 1.5
```{r}
# same to 1.1
head(sbuxPrices.df)
```

### 1.6
```{r}
# slice the 101-132 observations from the dataframe sbux.df
sbux.df[101:132,]
```

## 2
```{r}
sbux.df$Date = as.Date(sbux.df$Date)
plot(sbux.df$Date,sbux.df$Adj.Close,"l",col = "blue",xlab = "Date",ylab = "Price",main = "Price of SUBX from March 1998 to March 2013")
legend("topleft","SBUX",col="blue",lty=1)
```

## 3
```{r}
# get the simple returan and cc return
sbux.df  = sbux.df %>% mutate(
  Adj.Close_prior = lag(Adj.Close),
  simple_return = (Adj.Close-Adj.Close_prior)/Adj.Close_prior,
  cc_return = log(Adj.Close) - log(Adj.Close_prior)
)
# draw graphs seperately
plot(sbux.df$Date,sbux.df$simple_return,"l",col = "blue",xlab = "Date",ylab = "Return",main = "Simple Return of SUBX from March 1998 to March 2013")
legend("bottomright","Simple Return",col="blue",lty=1)
plot(sbux.df$Date,sbux.df$cc_return,"l",col = "blue",xlab = "Date",ylab = "Return",main = "CC Return of SUBX from March 1998 to March 2013")
legend("bottomright","CC Return",col="blue",lty=1)
```

```{r}
# draw together
plot(sbux.df$Date,sbux.df$simple_return,"l",col = "blue",xlab = "Date",ylab = "Return",main = "Return of SUBX from March 1998 to March 2013")
lines(sbux.df$Date,sbux.df$cc_return,col ="red")
legend("bottomright",c("Simple Return","CC Return"),col=c("blue","red"),lty=1)

```


